### 2017-04-04 paper/oopsla17-submission/learning.tex
some text about neural netwroks

Recall that we formulate the localization problem as a supervised
classification problem.
%
This means that we assume the existence of a training set
$D = \{\langle \mathbf{x}_i, y_i \rangle\}_{i=1}^{n}$
of sample inputs $\mathbf{x}$ and their corresponding labels $y$.
%
The learning task is to model the probability $Pr(y\ |\ \mathbf{x})$
of a label being assigned to a given input.

There are many learning algorithms to choose from, existing
on a spectrum that balances expressiveness with ease of training (and of
interpreting the learned model).
%
In this section we present four standard learning algorithms that we
will investigate:
%
(1) logistic regression,
(2) decision trees,
(3) random forests, and
(4) multi-layer perceptrons.
%
For each algorithm, we describe the form of the model it learns, the
training procedure, and any hyper-parameters that must be supplied by a
human.

\paragraph{Logistic regression}
% The simplest model we investigate is logistic regression, which learns a
% linear function of the features.
% %
% The goal is to learn a set of weights $W$ and biases $b$ such that the
% function
% %
% $$
% Pr(y\ |\ \mathbf{x}) = \frac{1}{1 + \mathsf{exp}(-W\mathbf{x} - b)}
% $$
% %
% effectively maps feature vectors $\mathbf{x}$ to labels $y$.

@@

The simplest model we investigate is logistic regression, which can be
understood in two steps.
%
First, we compute the \emph{evidence} for a label $y$ as a linear
function of the input $\mathbf{x}$, with a set of weights $w_i$ and a
bias $b$ that will be learned from the training set.
$$
\mathsf{ev} = \sum_i w_i \mathbf{x}_i + b
$$
Then we use the logistic function $f(x) = \frac{1}{1 + e^{-x}}$ to
compress the evidence term into the $[0,1]$ interval, which can then be
interpreted as the probability that the label $y$ should be applied.
%
This gives us the final model
$$
Pr(y\ |\ \mathbf{x}) = \frac{1}{1 + \mathsf{exp}(-\sum_i w_i \mathbf{x}_i - b)}
$$

@@

It has been observed \ES{CITE??} that large weights often coincide with
\emph{overfitting} of the model --- where the model performs well on the
training samples but not on the testing samples.
%
Thus, it is common to add a \emph{regularization} term to the cost
function, a popular choice is the L2 norm of the weights $\sum_i w_i^2$,
which has the effect of penalizing the model for learning large weights.
The contribution of the regularization term to the over cost function is
controlled by another hyper-parameter $\lambda$, often called the
regularization rate.

Logistic regression is popular for its ease of training and of
interpreting the resulting model; however, it can be limited in its
applicability.
%
As a generalized linear model, it may perform poorly when asked to
learn an inherently \emph{nonlinear} function.
%
This limitation can be mitigated to some extent by adding more features
to the model (\eg combinations of the existing features \ES{CITE?}), but
the fundamental issue remains.

\paragraph{Decision trees}
\ES{TODO: Maybe Huma?}

\paragraph{Random forests}
\ES{TODO: Maybe Huma?}

\paragraph{Neural networks}
The last (and most complex) model we discuss is Artificial Neural
Networks (ANN).

The fundamental building block of an ANN is the linear model, the
nonlinearity arises from the \emph{activation functions} that govern
whether an individual linear model propagates its signal to the next layer.

>>>>

Recall that we formulate type error localization as a supervised
classification problem.
%
This means that we assume the existence of a training set
$S = \{\langle \mathbf{x}_i, y_i \rangle\}_{i=1}^{n}$
of sample inputs $\mathbf{x}$ and their corresponding labels $y$.
%
The learning task is to model the probability $Pr(y\ |\ \mathbf{x})$
of a label being assigned to a given input.

There are many learning algorithms to choose from, existing
on a spectrum that balances expressiveness with ease of training (and of
interpreting the learned model).
%
In this section we present four standard learning algorithms that we
will investigate:
%
(1) logistic regression,
(2) decision trees,
(3) random forests, and
(4) neural networks.
%
For each algorithm, we describe the form of the model it learns, the
training procedure, and any hyper-parameters that must be supplied by a
human.

\paragraph{Logistic Regression}
% The simplest model we investigate is logistic regression, which learns a
% linear function of the features.
% %
% The goal is to learn a set of weights $W$ and biases $b$ such that the
% function
% %
% $$
% Pr(y\ |\ \mathbf{x}) = \frac{1}{1 + \mathsf{exp}(-W\mathbf{x} - b)}
% $$
% %
% effectively maps feature vectors $\mathbf{x}$ to labels $y$.

@@

The simplest model we investigate is logistic regression, which can be
understood in two steps.
%
First, we compute the \emph{evidence} for a label $y$ as a linear
function of the feature vector $\mathbf{x}$, using a weight vector
$\mathbf{w}$ and a bias $b$ that will be learned from the training set.
$$
\mathsf{ev} = \sum_j w_j x_j + b
$$
Then we use the logistic function (also called a sigmoid function)
$\sigma(x) = 1 / (1 + e^{-x})$ to compress the evidence term into the
$[0,1]$ interval, which can then be interpreted as the probability that
the label $y$ should be applied.
%
This gives us the final model:
$$
Pr(y\ |\ \mathbf{x}) = \frac{1}{1 + \mathsf{exp}(-\sum_j w_j x_j - b)}
$$

@@

It has been observed \ES{CITE??} that large weights often coincide with
\emph{overfitting} of the model --- where the model performs well on the
training samples but not on the testing samples.
%
Thus, it is common to add a \emph{regularization} term to the cost
function, a popular choice is the $L_2$ norm of the weights $\sum_j w_j^2$,
which has the effect of penalizing the model for learning large weights.
The contribution of the regularization term to the overall cost function is
controlled by another hyper-parameter $\lambda$, often called the
regularization rate.

As a generalized linear model, logistic regression is popular for its
ease of training and of interpreting the resulting model; however, it
can be limited in its applicability.
%
In particular, it may perform poorly when asked to learn an inherently
\emph{nonlinear} function.
%
This limitation can be mitigated to some extent by adding more features
to the model (\eg combinations of the existing features \ES{CITE?}), but
the fundamental issue remains.

\paragraph{Decision Trees}
\ES{TODO: Maybe Huma?}

\paragraph{Random Forests}
\ES{TODO: Maybe Huma?}

\paragraph{Neural Networks}
The last (and most complex) model we discuss is a type of neural network
called a \emph{multi-layer perceptron} \ES{CITE}.
%
Neural networks can be understood as a collection of linear models, just
like the one used in logistic regression, arranged in a directed graph.
%
Each node in the graph corresponds to a single linear model, called a
\emph{neuron}, and the edges propagate signals from the input features,
through the neurons, to the output labels.
%
The linear model in each neuron is wrapped in an \emph{activation
  function}, which controls whether (or how strongly) the signal will be
propagated out.
%
These activation functions are what allow neural networks to accurately
model nonlinear functions.
%
A common choice of activation function is the same sigmoid function
used by logistic regression, alternatives include the hyperbolic $\tanh$
function, and more recently the \emph{rectified linear unit} (ReLU)
$f(x) = \mathsf{max}(0,x)$ \ES{CITE}.

The neurons are arranged in \emph{layers}; each layer contains a set of
neurons that take in signals from the previous layer and propagate
signals to the next layer.
%
The number of layers, the number of neurons per layer, and the
connections between layers constitute the \emph{architecture} of a
neural network, and are all important hyper-parameters.
%
We consider a particular class of neural networks called
\emph{multi-layer perceptrons} (MLP), where the layers a fully connected to
each other, \ie each neuron propagates its signal to every neuron in the
subsequent layer.
%
We will only consider MLPs with a single layer of neurons, but we will
vary the number of neurons in our experiments.

Neural networks are trained similarly to logistic regression using
stochastic gradient descent, and thus the learning rate $\eta$ and
regularization rate $\lambda$ are also important hyper-parameters.

\ES{should mention that logistic regression can be thought of as a degenerate MLP with 0 layers, and perhaps add a diagram?}

\ES{need to say something about neurons corresponding to ``hidden'' features, give intuition..}

% The fundamental building block of an ANN is the linear model, the
% nonlinearity arises from the \emph{activation functions} that govern
% whether an individual linear model propagates its signal to the next layer.
